Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modelling

### 2022-06-27 gibbs.tex
LN: abstract

\begin{document}
\begin{abstract}
Recently polyelectrolyte hydrogels have been proposed as draw agents
for reverse osmosis desalination techniques. Indeed, polyelectrolyte
hydrogels have the ability to absorb a big amount of water across
forward osmosis membrane as a result of their swelling pressure. The
insoluble cross-linked network of the gel enables dewatering under
the influence of a stimuli (thermal and/or mechanical). On the other
hand, the network structure of a polymer hydrogel from a thermodynamic
perspective is already an osmotic membrane. So hydrogel microparticles
may allow to completely avoid the osmotic membranes in forward osmosis
and use microfiltration instead. By this article, we present our recent
theoretical study of the use of polyelectrolyte hydrogel for water
desalination. We modeled the thermodynamic equilibrium of coexistence
of the gel and the aqueous salt solution in the so-called closed ensemble,
in which the total amount of ions is assumed to be constant. We modeled
the compression of the gel and the associated with that release of
the solution. We have shown that the squeezed out solution has a little
lower salinity than that the gel was equilibrated with. Also, we performed
a set of simulations modeling the process of continuous decrease of
water salinity up to freshwater concentrations.

>>>>

\begin{document}
\begin{abstract}
Recently polyelectrolyte hydrogels have been proposed as draw agents
for reverse osmosis desalination techniques. Indeed, polyelectrolyte
hydrogels have the ability to absorb a big amount of water across
forward osmosis membrane as a result of their swelling pressure. The
insoluble cross-linked network of the gel enables dewatering under
the influence of a stimulus (thermal and/or mechanical). On the other
hand, the network structure of a polymer hydrogel, from a thermodynamic
perspective, is already an osmotic membrane. So hydrogel microparticles
may allow to completely avoid the osmotic membranes in forward osmosis
and use microfiltration instead.

In this article, we present our recent
theoretical study of the use of polyelectrolyte hydrogel for water
desalination. We modeled the thermodynamic equilibrium of coexisting
gel and aqueous salt solution phases in the so-called closed ensemble,
in which the total amount of ions is assumed to be constant. We modeled
the compression of the gel associated with the release of
solution. We have shown that the squeezed out solution has a little
lower salinity than the one the gel was equilibrated with. Finally, we performed
a set of simulations modeling the process of continuous decrease of
water salinity up to freshwater concentrations.
